\section{Meetings of the committee}
\label{rule:committeeMeetings}

\begin{enumerate}
	\item \label{subrule:committeeMeetings:regularity} The committee is to meet at least once in each month at any place and time the committee determines.
	\item A meeting of the committee, other than a meeting referred to in subrule \ref{subrule:committeeMeetings:regularity}, may be convened by the president or any 4 of the members of the committee.
	\item \label{subrule:committeeMeetings:notice} Written notice of any special committee meeting is to be served on members of the committee and is to specify the general nature of the business to be transacted.
	\item A special committee meeting may only transact business of which notice is given in accordance with subrule \ref{subrule:committeeMeetings:notice}.
	\item A quorum for the transaction of the business of a meeting of the committee is 6 members of the committee.
	\item Business is not to be transacted at a meeting of the committee unless a quorum is present.
	
	\item If a quorum is not present within half an hour after the time appointed for the commencement of --
	\begin{enumerate}
		\item a meeting of the committee (other than a special committee meeting), the meeting is to be adjourned to the same day in the next week at the same time and at the same place; or
		\item a special committee meeting, the meeting is dissolved.
	\end{enumerate}
	
	\item At each meeting of the committee, the chairperson is to be --
	\begin{enumerate}
		\item the president; or
		\item in the absence of the president, the senior vice-president; or
		\item in the absence of the president and the senior vice-president, the other vice-president; or
		\item in the absence of the president and both vice-presidents, a member of the committee elected to preside as chairperson by the members of the committee present at the meeting.
	\end{enumerate}
	
	\item Any question arising at a meeting of the committee is to be determined --
	\begin{enumerate}
		\item on a show of hands; or
		\item if demanded by a member, by a poll taken at that meeting in the manner the chairperson determines.
	\end{enumerate}
	
	\item \label{subrule:committeeMeetings:voteWeight} On any question arising at a meeting of the committee, a member of the committee (including the chairperson) has one vote only.
	\item Despite subrule \ref{subrule:committeeMeetings:voteWeight}, in the case of an equality of votes, the chairperson has a second or casting vote.

	\item Written notice of each committee meeting is to be served on each member of the committee by --
	\begin{enumerate}
		\item giving it to the member during business hours before the day on which the meeting is to be held; or
		\item leaving it, during business hours before the day on which the meeting is to be held, at the member's postal or residential address or place or address of business or employment last known to the server of the notice; or
		\item sending it by post, to the person's postal or residential address or address of business or employment last known to the server of the notice, in sufficient time for it to be delivered to that address in the ordinary course of post before the day on which the meeting is to be held; or
		\item faxing it to the member's fax number; or
		\item emailing it to the email address, of the member, that the member has nominated as the email address to which notices from the Association may be sent.
	\end{enumerate}
\end{enumerate}